---
title: "Big Mark Sales"
author: "Jackie Chan"
date: "January 20, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      fig.width = 8, fig.height = 6, fig.align = "center")
```

# Content
#####1.Data Preparation
######1.1 Data Source
######1.2 Load the Dataset & Required Packages
######1.3 Data Preparation
######1.4 Basic Summary of the Dataset

#####2.Exploratory Data Analysis
######2.1 Item Sales in term of
######2.2 Item Sales in term of
######2.3 Item Sales in term of
######2.4 Item Sales in term of

#####3.Insights & Conclusion

# 1.Data Preparation

###1.1 Data Source: 
1. From this link: https://datahack.analyticsvidhya.com/contest/practice-problem-big-mart-sales-iii/
2. Download the "Train File" and "Test File"
3. Save them to your working directory

* All the codes have been saved in another file, "Codes.R".
* All the exploratory data analysis was based on the "Train File".

###1.2 Load the Dataset & Required Packages

* This project will use three R packages, i.e. tidyverse, gridExtra, hexbin.

```{r Load Dataset}
setwd("D:/Jackie/Documents/Data Science Projects/20180124 BigMartSales/2. Prepared Data")
martdataset_train <- read.csv("Train_UWu5bXk.csv")
martdataset_test <- read.csv("Test_u94Q5KV.csv")
```

```{r Load Package}
library(tidyverse)
library(gridExtra)
library(hexbin)
```

###1.3 Data Preparation

* Missing values have been imputed
* Mislabeled observations have been corrected
* New variable has been created
* For the variable, Item_Fat_Content, "LF" and "low fat" have been changed to "Low Fat"; "reg" has been changed to "Regular"
* For the variable, Outlet_Size, missing values of "" have been replaced with NAs
* For the variable, Item_Weight, missing values of NAs have been replaced by the mean
* New variable, Log2_MRP, has been created for better comparison of retail price

```{r Data Preparation}
martdataset_test$Item_Outlet_Sales <- rep(NA, nrow(martdataset_test))
martdataset <- rbind(martdataset_train, martdataset_test)

for (i in 1:length(martdataset$Item_Fat_Content)){
        if (martdataset$Item_Fat_Content[i] %in% c("LF", "low fat")){
                martdataset$Item_Fat_Content[i] <- "Low Fat"    
        } else if (martdataset$Item_Fat_Content[i] %in% c("reg")){
                martdataset$Item_Fat_Content[i] <- "Regular"
        }
}
martdataset$Item_Fat_Content <- factor(as.character(martdataset$Item_Fat_Content))
                                       
#> Change the "" in the outlet_size to NA
martdataset$Outlet_Size <- as.character(martdataset$Outlet_Size)
martdataset$Outlet_Size <- ifelse(martdataset$Outlet_Size %in% c(""), 
                                  NA, 
                                  martdataset$Outlet_Size)
martdataset$Outlet_Size <- factor(martdataset$Outlet_Size)

#> Compute NA in item_weight by its mean value
martdataset$Item_Weight <- ifelse(is.na(martdataset$Item_Weight), 
                                  mean(martdataset$Item_Weight, na.rm = T), 
                                  martdataset$Item_Weight)
#>>> Create new variable, Log2_MRP, for easy comparison of retail price
martdataset <- martdataset %>%
        mutate(Log2_MRP = log2(Item_MRP))

#>>> Re-arrange the columns
sale <- martdataset %>% 
        select(Item_Outlet_Sales)
no_sale <- martdataset %>% 
        select(everything(), -Item_Outlet_Sales)
martdataset <- cbind(no_sale, sale)

#>>> Separate into training set and test set
martdataset_train <- martdataset[1:8523, ]
martdataset_test <- martdataset[8524:14204, -13]
rm(martdataset, sale, no_sale)
martdataset_train <- as_tibble(martdataset_train)
martdataset_test <- as_tibble(martdataset_test)
```

###1.4 Basic Summary of the Dataset
BigMart has collected 2013 sales data for 1559 products across 10 stores in different cities. In our training dataset, we have 8523 observations and 12 variables. Also, there is one additional variable which has been transformed from one of the original variables.

The structure of the data is as below:
```{r head of data}
str(martdataset_train)
```

The numeric summary of the data is as below:
```{r numeric summary}
summary(martdataset_train)
```

#2.Exploratory Data Analysis
Let's begin our data analysis by asking a question regarding to the item sales. What is the distribution of item sales look like?
```{r distribution of item sales}
figure1a <- martdataset_train %>% 
        ggplot(aes(x = Item_Outlet_Sales)) +
        geom_histogram(binwidth = 500, color = "white") +
        xlab("Item Sales") +
        ggtitle("The Distribution of Item Sales")
figure1b <- martdataset_train %>% 
        ggplot(aes(x = Item_Outlet_Sales)) +
        geom_histogram(binwidth = 500, color = "white") +
        coord_cartesian(ylim = c(0, 25)) + 
        xlab("Item Sales") +
        ggtitle("Zoom in the y-axis of the Distribution of Item Sales")
grid.arrange(figure1a, figure1b)
```

* The overall distribution of item sales is right skewed
* More low item sales than high item sales
* The first bin (-250 to 250) is dramatically lower than the second bin
* Outliers of item sales are found, which are beyond 7500
* Those outliers, though have little in count, contain higher item sales

The above points will be addressed one by one. So...
##### Why the overall distribution of item sales is right skewed?

###2.1 Item Sales in term of

###2.2 Item Sales in term of

###2.3 Item Sales in term of

###2.4 Item Sales in term of

#3.Insights & Conclusion
