---
title: "Personal_Project_Big_Mark_Sales"
author: "Jackie Chan Lit King"
date: "January 20, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      fig.width = 8, fig.height = 6, fig.align = "center")
```

# Content
#####1.Data Preparation
######1.1 Data Source
######1.2 Load the Dataset & Required Packages
######1.3 Data Preparation
######1.4 Basic Summary of the Dataset

#####2.Exploratory Data Analysis
######2.1 Item Sales in term of
######2.2 Item Sales in term of
######2.3 Item Sales in term of
######2.4 Item Sales in term of

#####3.Insights & Conclusion

# 1.Data Preparation

###1.1 Data Information: 
1. From this link: https://datahack.analyticsvidhya.com/contest/practice-problem-big-mart-sales-iii/
2. Download the "Train File" and "Test File"
3. Save them to your working directory

##### Notes:
* All the exploratory data analysis was based on the "Train File".
* Graphic presentation of this project is in this link: http://rpubs.com/funnychan01/354026

###1.2 Load the Dataset & Required Packages

* This project will use three R packages, i.e. tidyverse, gridExtra, hexbin.

```{r Load Dataset}
# Please set your own working directory
# Dataset is from this link: https://datahack.analyticsvidhya.com/contest/practice-problem-big-mart-sales-iii/
setwd("D:/Jackie/Documents/Data Science Projects/20180124 BigMartSales/2. Prepared Data")
martdataset_train <- read.csv("Train_UWu5bXk.csv")
martdataset_test <- read.csv("Test_u94Q5KV.csv")
```

```{r Load Package}
library(tidyverse)
library(gridExtra)
library(hexbin)
```

###1.3 Data Preparation

* Missing values have been imputed
* Mislabeled observations have been corrected
* New variable has been created
* For the variable, Item_Fat_Content, "LF" and "low fat" have been changed to "Low Fat"; "reg" has been changed to "Regular"
* For the variable, Outlet_Size, missing values of "" have been replaced with NAs
* For the variable, Item_Weight, missing values of NAs have been replaced by the mean
* New variable, Log2_MRP, has been created for better comparison of retail price

```{r Data Preparation}
martdataset_test$Item_Outlet_Sales <- rep(NA, nrow(martdataset_test))
martdataset <- rbind(martdataset_train, martdataset_test)

#> change "LF" and "low fat" to "Low Fat"
#> change "reg" to "Regular"
for (i in 1:length(martdataset$Item_Fat_Content)){
        if (martdataset$Item_Fat_Content[i] %in% c("LF", "low fat")){
                martdataset$Item_Fat_Content[i] <- "Low Fat"    
        } else if (martdataset$Item_Fat_Content[i] %in% c("reg")){
                martdataset$Item_Fat_Content[i] <- "Regular"
        }
}
martdataset$Item_Fat_Content <- factor(as.character(martdataset$Item_Fat_Content))
                                       
#> Change the "" in the outlet_size to NA
martdataset$Outlet_Size <- as.character(martdataset$Outlet_Size)
martdataset$Outlet_Size <- ifelse(martdataset$Outlet_Size %in% c(""), 
                                  NA, 
                                  martdataset$Outlet_Size)
martdataset$Outlet_Size <- factor(martdataset$Outlet_Size)

#> Compute NA in item_weight by its mean value
martdataset$Item_Weight <- ifelse(is.na(martdataset$Item_Weight), 
                                  mean(martdataset$Item_Weight, na.rm = T), 
                                  martdataset$Item_Weight)
#>>> Create new variable, Log2_MRP, for easy comparison of retail price
martdataset <- martdataset %>%
        mutate(Log2_MRP = log2(Item_MRP))

#>>> Re-arrange the columns
sale <- martdataset %>% 
        select(Item_Outlet_Sales)
no_sale <- martdataset %>% 
        select(everything(), -Item_Outlet_Sales)
martdataset <- cbind(no_sale, sale)

#>>> Separate into training set and test set
martdataset_train <- martdataset[1:8523, ]
martdataset_test <- martdataset[8524:14204, -13]
rm(martdataset, sale, no_sale)
martdataset_train <- as_tibble(martdataset_train)
martdataset_test <- as_tibble(martdataset_test)
```

###1.4 Basic Summary of the Dataset
BigMart has collected 2013 sales data for 1559 products across 10 stores in different cities. In our training dataset, we have 8523 observations and 12 variables. Also, there is one additional variable which has been transformed from one of the original variables.

The structure of the data is as below:
```{r head of data}
str(martdataset_train)
```

The numeric summary of the data is as below:
```{r numeric summary}
summary(martdataset_train)
```

#2.Exploratory Data Analysis
Let's begin our data analysis by asking a question regarding to the item sales. 

###2.1 What is the distribution of item sales look like?
```{r distribution of item sales}
figure1a <- martdataset_train %>% 
        ggplot(aes(x = Item_Outlet_Sales)) +
        geom_histogram(binwidth = 500, color = "white") +
        xlab("Item Sales") +
        ggtitle("Fig.1a The Distribution of Item Sales")
figure1b <- martdataset_train %>% 
        ggplot(aes(x = Item_Outlet_Sales)) +
        geom_histogram(binwidth = 500, color = "white") +
        coord_cartesian(ylim = c(0, 25)) + 
        xlab("Item Sales") +
        ggtitle("Fig.1b Zoom in the y-axis of the Distribution of Item Sales")
grid.arrange(figure1a, figure1b)
```

* The overall distribution of item sales is right skewed
* More low item sales than high item sales
* The first bin (-250 to 250) is dramatically lower than the second bin
* The second bin (250 to 750) contains the highest in count of item sales
* Outliers of item sales are found, which are beyond 7500
* Those outliers, though have little in count, contain higher item sales

The above points will be addressed one by one. So...

####2.1.1 Why the overall distribution of item sales is right skewed?
Firstly, I will create histograms for each continuous variables.

```{r histograms of each continuous var}
figure1c <- martdataset_train %>% 
                ggplot(aes(x = Item_Weight)) +
                geom_histogram(binwidth = 1, color = "white") +
                ggtitle("Fig.1c The Distribution of Item Weight") +
                xlab("Item Weight")
figure1d <- martdataset_train %>% 
                ggplot(aes(x = Item_Visibility)) +
                geom_histogram(binwidth = 0.01, color = "white") +
                ggtitle("Fig.1d The Distribution of Item Visibility") +
                xlab("Item Visibility")
figure1e <- martdataset_train %>% 
                ggplot(aes(x = Item_MRP)) +
                geom_histogram(binwidth = 10, color = "white") +
                ggtitle("Fig.1e The Distribution of Item Maximum Retail Price") +
                xlab("Item Maximum Retail Price")
grid.arrange(figure1c, figure1d, figure1e)
```

From the above three plots, one of them is also right-skewed in distribution and is similar to the distribution of item sales, i.e. item visibility. Does that imply the correlation between item visibility and item sales? Let's assume the higher the visibility, the higher the sales. 

```{r visibility vs sales}
figure1f <- martdataset_train %>% 
        ggplot(aes(y = Item_Visibility, x = Item_Outlet_Sales)) +
        geom_hex() +
        ggtitle("Fig.1f The Relationship between Item Visibility and Item Sales") +
        xlab("Item Sales") +
        ylab("Item Visibility")
figure1g <- martdataset_train %>% 
        ggplot(aes(x = cut_width(Item_Visibility, 0.05), y = Item_Outlet_Sales)) +
        geom_jitter(alpha = 0.05) +
        geom_boxplot(varwidth = T, aes(color = cut_width(Item_Visibility, 0.05)), show.legend = F) +
        ggtitle("Fig.1g The Relationship between Item Visibility and Item Sales") +
        xlab("Item Visibility") +
        ylab("Item Sales") + 
        coord_flip()
grid.arrange(figure1f, figure1g, ncol = 1)
```

Fig.1f and 1g shows a quite counterintuitive result of their relationship. Most of the items clustter at the bottom left, meaning less visible and less sales. Also, items with visibility less than 0.1 have achieved sales up to 10000. Yet, items with visibility greater than 0.2 only have sales less than 1000, though the items fall in this clustter are less in count. Maybe there are some hidden facts behind the scene. We will go into depth in the later session. 

* Follow-up 1 - Fig.1f: The clustter of item visibility

How about the relationship between item sales and retail price? Will that be the higher in retail price, the higer in item sales?

```{r sales vs retail price}
figure1h <- martdataset_train %>% 
        ggplot(aes(y = Item_Outlet_Sales, x = Item_MRP)) +
        geom_point(alpha = 0.1, color = "blue", fill = "skyblue") +
        geom_smooth(color = "red") +
        xlab("Item Maximum Retail Price") +
        ylab("Item Sales") +
        ggtitle("Fig.1h The Relationship between Item Sales and Item Retail Price")
figure1i <- martdataset_train %>% 
        ggplot(aes(y = Item_Outlet_Sales, x = cut_width(Item_MRP, 50))) +
        geom_jitter(alpha = 0.1, color = "blue", fill = "skyblue") +
        geom_boxplot(varwidth = T, show.legend = F,aes(color = cut_width(Item_MRP, 50)))+
        xlab("Item Maximum Retail Price") +
        ylab("Item Sales") +
        ggtitle("Fig.1i The Relationship between Item Sales and Item Retail Price")
grid.arrange(figure1h, figure1i)
```

There's a distribution pattern in Fig.1h. The retail price divides into 4 clustters with a obvious boundary between each clustters. Also, the plot confirms our assumption about the relationship between these two variables. Item sales increase as retail pice increases. Fig.1i show that the variation increases as the retail price increases. We may wonder such different variations were due to some reasons, such as different product types, different stores strategies, etc. Thus, further investigation has to be conducted. In short, item's maximum retail price might be a strong predictive in the model predicting item sales.

* Follow-up 2 - Fig.1h: The clustter of item retail price

Up to here, we have not yet found out the reason of the right-skewed distribution of item sales. Let's check the relationship between item weight and item sales.

```{r sales vs weight}
figure1j <- martdataset_train %>% 
        ggplot(aes(x = Item_Weight, y = Item_Outlet_Sales)) +
        geom_point(alpha = 0.1)+
        xlab("Item Weight") +
        ylab("Item Sales") +
        ggtitle("Fig.1j The Relationship between Item Sales and Item Weight")
grid.arrange(figure1j, figure1c)
```

Fig.1c and 1j shows a strange pattern in the plots. There's a darker vertical line at the middle of both plots. Excluding this fact, the relationship between sales and weight is not obvious. For that mentioned vertical line, we have to investigate further.

* Follow-up 3 - Fig.1c: Strange vertical line at the middle of the distribution of item weight

Back to our question, the right-skewed distribution of item sales is not explained by item weight, item visibilty nor item retail price. How about we break the distribution of item sales by facet of categorical variables?

```{r sales facet by fat content}
figure1a + facet_wrap(~ Item_Fat_Content) + ggtitle("Fig.1k The Distribution of Item Sales v.s. Item Fat Content")
figure1a + facet_wrap(~ Item_Type) + ggtitle("Fig.1l The Distribution of Item Sales v.s. Item Type")
figure1a + facet_wrap(~ Outlet_Identifier) + ggtitle("Fig.1m The Distribution of Item Sales v.s. Outlet ID")
figure1a + facet_wrap(~ Outlet_Establishment_Year) + ggtitle("Fig.1n The Distribution of Item Sales v.s. Establishment Year")
figure1a + facet_wrap(~ Outlet_Size) + ggtitle("Fig.1o The Distribution of Item Sales v.s. Outlet Size")
figure1a + facet_wrap(~ Outlet_Location_Type) + ggtitle("Fig.1p The Distribution of Item Sales v.s. Outlet Location Type")
figure1a + facet_wrap(~ Outlet_Type) + ggtitle("Fig.1q The Distribution of Item Sales v.s. Outlet Type")
```

By plotting item sales against different categorical variables, we still cannot find out the reason accounting for such right-skewed distribution. We may wonder that either the dataset is insufficient to provide the answer or it is due to coincidence. 

From Fig.1k, the shape of distribution is similar. The plot shows there is more low fat item than regular item.

From Fig.1m, it reveals something interesting. Store 010 and store 019 has sales concentrating to the far left, meaning that most of the items in these two stores have low sales performance. That may account for the right-skewed distribution of the overall item sales. Yet, by excluding them from the plot, the shape of distribution does not change much. It can be illustrated by the following plot, Fig.1r.

```{r exclude OUT010 OUT019}
martdataset_train %>% 
        filter(Outlet_Identifier != "OUT010", Outlet_Identifier != "OUT019") %>% 
        ggplot(aes(x = Item_Outlet_Sales)) +
        geom_histogram(binwidth = 500, color = "white") +
        xlab("Item Sales") +
        ggtitle("Fig.1r The Distribution of Item Sales Excluding Store 010 & 019")
```

From Fig.1n, there's nothing interesting here. Since we have 10 stores in our dataset and they are correlated with their establishment year, the distribution of item sales against establishment year looks similar to that against stores ID of Fig.1m. This also explains the shape of distribution in Fig.1o, 1p and 1q.

From Fig.1o, there is another counterintuitive fact here, i.e. larger outlet size does not imply higher item sales.

From Fig.1q, the shape of distribution of item sales in grocery items looks familiar to us. We may wonder outlet 010 and outlet 019 belongs to that category. Let's find out:

```{r oultet 010 019 is grocery}
martdataset_train %>% 
        filter(Outlet_Type == "Grocery Store") %>% 
        group_by(Outlet_Type, Outlet_Identifier) %>% 
        summarise(count = n())
```

####2.1.2 Why the first bin behaves like that?
####2.1.3 What are the outliers indicate for?

###2.2 Follow-up of section 2.1

####2.2.1 Follow-up 1 - Fig.1f: The clustter of item visibility
####2.2.2 Follow-up 2 - Fig.1h: The clustter of item retail price
####2.2.3 Follow-up 3 - Fig.1c: Strange vertical line at the middle of the distribution of item weight

#3.Insights & Conclusion
